Data Preparation - Course Catalogues

### 2019-04-12 Data Preparation - Course Catalogues.Rmd
identify list of courses currently offered
fixes bug in UCV

remove_header_UCV <- function(string) string %>% str_sub(29, -1)

overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses")
overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\r\n *Maastricht Science Programme")

>>>>

remove_header_UCV <- function(string) string %>% str_sub(28, -1)

overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses")
overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme")
